Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-17 paper.qmd
Added quarto citation
Figure 11 resized axes cricle..

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 3, 
                            scaled_data = scaled_gau_data, 
                            scaled_data_model = scaled_gau_data_model, 
                            distance_df_small_edges = distance_df_small_edges, 
                            axis_param = list(limits = 1.2,
                                              axis_scaled = 2,
                                              axis_pos_x = -1.1, 
                                              axis_pos_y = -1.1, 
                                              threshold = 0.05))

@@

These `R` packages were used for the work: `tidyverse` (@hadley2019), `Rtsne` (@jesse2015), `umap` (@tomasz2023), `patchwork` (@thomas2024), `colorspace` (@achim2020), `langevitour` (@harisson2024), `conflicted` (@hadley2023), `reticulate` (@kevin2024), `kableExtra` (@hao2024). These `python` packages were used for the work: `trimap` (@amid2019) and `pacmap` (@yingfan2021). The article was created with `R` packages `rticles` (@jjallaire2024), `knitr` (@yihui2014), and `rmarkdown` (@yihui2020). The project's GitHub repository ([https://github.com/JayaniLakshika/paper-nldr-vis-algorithm](https://github.com/JayaniLakshika/paper-nldr-vis-algorithm)) contains all materials required to reproduce this article.

>>>>

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 3, 
                            scaled_data = scaled_gau_data, 
                            scaled_data_model = scaled_gau_data_model, 
                            distance_df_small_edges = distance_df_small_edges, 
                            axis_param = list(limits = 1.5,
                                              axis_scaled = 2,
                                              axis_pos_x = -1, 
                                              axis_pos_y = -1, 
                                              threshold = 0.05))

@@

These `R` packages were used for the work: `tidyverse` (@hadley2019), `Rtsne` (@jesse2015), `umap` (@tomasz2023), `patchwork` (@thomas2024), `colorspace` (@achim2020), `langevitour` (@harisson2024), `conflicted` (@hadley2023), `reticulate` (@kevin2024), `kableExtra` (@hao2024). These `python` packages were used for the work: `trimap` (@amid2019) and `pacmap` (@yingfan2021). The article was created with `R` packages `quarto` (@jjallaire2024). The project's GitHub repository ([https://github.com/JayaniLakshika/paper-nldr-vis-algorithm](https://github.com/JayaniLakshika/paper-nldr-vis-algorithm)) contains all materials required to reproduce this article.
